TEXT MINING DESCRIPTIONS OF DREAMS: AESTHETIC AND CLINICAL EFFORTS

### 2017-08-29 article/article.tex
incorporada sugestao da revisao enmc

	This text was obtained through picking only the first and last words of each sentence.}\label{tab:comecoFinal}

>>>>

	This text was obtained through picking only the first and last words of each sentence.
	As illustrated in this text, the unusual (and formally wrong) morphological and syntactic
	constructions were used for enhanced artistic expression
	and as clinical evidence of complex cognitive elaborations.}\label{tab:comecoFinal}
